On the specific recursive structure of iterated parametricity

### 2025-11-11 paper/paper.tex
Add for all p in previous nuset record for mscs
Structuring the construction into subsections

@@

\begin{align*}
  \framep[n][p]      & : \U                                                                                                                 \\
  \framep[n-1][p]    & :  \U                                                                                                                \\
  \framep[n-2][p]    & : \U                                                                                                                 \\
  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   \\
  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 \\                                                                 \\
  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] =                              \\
                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                                                \\
  \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
  \\
  \mathsf{hypFS0}    & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              \\
  \mathsf{hypPrevF}  & : \framep[n-1][0]                                                                                       = \unitpoint \\
  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    \\
  \mathsf{hypRF0}    & : \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                          \\
  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            \\
  \ldots             & \;\;\;\;\texttt{fields for painting, restrf, cohp}
\end{align*}

@@

To talk about sequences of $\framep$, $\painting$ or $\restrf$, we need to specify their types. The type of $\restrf$ will be defined mutually with $\framep$ of the same level, but the type of $\framep$, $\painting$ can be defined in advance, the second one being however dependent on the first one. In general, components of such sequences will have a type dependent on the previous components of the sequence, as it is the case for $\restrf$. So, the type of a sequence of length $p$ will be expressed as a $n$-iterated $\Sigma$-type. In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used. If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component. We can now define the types of sequences of $\framep$ and $\painting$ as follows:

@@

Formally, this can be described as: (NOTE: in frame, p should be understood as (p+1)-1)

@@

    \framep[n+1][0,...,p]                                                                    &

@@

@@

@@

@@

@@

\section{...}

@@

@@

@@

>>>>

\section{Outline of the recursive structure of iterated parametricity construction}

@@

\begin{align*}
  \framep[n][p]      & : \U & \mbox{for all $p\leq n$}                                                                                      \\
  \framep[n-1][p]    & : \U & \mbox{for all $p\leq n-1$}                                                                                    \\
  \framep[n-2][p]    & : \U & \mbox{for all $p\leq n-2$}                                                                                    \\
  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p] & \mbox{for all $p\leq n$}                        \\
  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p] & \mbox{for all $p\leq n-1$}                    \\
  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] =                              \\
                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1] & \mbox{for all $p\leq n$}                     \\
  \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
  \\
  \mathsf{hypFS}     & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d)) & \mbox{for all $p\leq n-1$} \\
  \mathsf{hypPrevF0} & : \framep[n-1][0]                                                                                       = \unitpoint \\
  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d)) & \mbox{for all $p\leq n-2$}    \\
  \mathsf{hypRF0}    & : \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                          \\
  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS} & \mbox{for all $p\leq n-1$}               \\
  \ldots             & \;\;\;\;\texttt{fields for painting, restrf, cohp}
\end{align*}

@@

To talk about sequences of $\framep$, $\painting$ or $\restrf$, we need to specify their types. The type of $\restrf$ will be defined mutually with $\framep$ of the same level, but the type of $\framep$, $\painting$ can be defined in advance, the second one being however dependent on the first one. In general, components of such sequences will have a type dependent on the previous components of the sequence, as it is the case for $\restrf$. So, the type of a sequence of length $p$ will be expressed as a $n$-iterated $\Sigma$-type. In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used. If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component.

\section{The construction}

\subsection{Specifying frames and paintings}

We can now define the types of sequences of $\framep$ and $\painting$ as follows:

@@

\subsection{Defining frames and specifying frame restrictions}

Frames are defined mutually with the types of frame restrictions,
using auxiliary definitions for the types and definitions of layers:

@@

    \framep[n+1][0,...,(p+1)-1]                                                                    &

@@

\subsection{Defining paintings}

@@

\subsection{Specifying painting restrictions}

@@

\subsection{Defining frame restrictions and specifying frame coherence laws}

@@

\subsection{Defining painting restrictions}

@@

\subsection{Specifying painting coherence laws}

@@

\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}

@@

\subsection{Defining painting coherence laws}

@@

\subsection{Completing the construction by induction}
